---
title: "brettFinalProject"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(tidyr)
library(plotly)
```

## Do some institutions disproportionately weigh ACT score over SAT score for admissions or vice versa?
Important columns from the original dataset: 
  Name

  Applicants total
  Admissions total

  Percent of freshmen submitting SAT scores
  Percent of freshmen submitting ACT scores

  SAT Critical Reading 25th percentile score
  SAT Critical Reading 75th percentile score
  SAT Math 25th percentile score
  SAT Math 75th percentile score	
  ACT Composite 25th percentile score
  ACT Composite 75th percentile score

Important values from other sources: 
  National average ACT score: 20.9 https://blog.prepscholar.com/average-act-score-for-2015-2014-2013-and-earlier-years
  National average SAT scores: 496 reading, 514 math https://www.studypoint.com/ed/average-sat-scores/
  National average SAT composite for math/reading: 505

New columns I will add for analysis:
  2 New columns for SAT reading/math composite 25th and 75th percentiles
  2 New columns for approximate ACT/SAT averages: (25th percentile + 75th percentile)/2
  2 New columns for the percent difference from national average: [(approximate average)-(national average)]/total points
  1 New column for ACT bias: (SAT percent difference)-(ACT percent difference)
  1 New column for SAT bias: (ACT percent difference)-(SAT percent difference)

Order by schools with the most bias to see if some schools have a heavy towards one test or the other. 

``` {r}
IPEDS <- readxl::read_xlsx('IPEDS_data.xlsx', sheet = 'Data')
IPEDSQ1 <- IPEDS %>%
  select('Name', 'Applicants total','Admissions total','Percent of freshmen submitting SAT scores','Percent of freshmen submitting ACT scores',
         'SAT Critical Reading 25th percentile score', 'SAT Critical Reading 75th percentile score', 'SAT Math 25th percentile score',
         'SAT Math 75th percentile score', 'ACT Composite 25th percentile score', 'ACT Composite 75th percentile score') 

names(IPEDSQ1) <- c("Name", "Applicants","Admissions","PctSAT","PctACT","SATRead25","SATRead75","SATMath25","SATMath75","ACT25","ACT75")

IPEDSQ1 <- na.omit(IPEDSQ1)

IPEDSQ1$SATMathAvg = (IPEDSQ1$SATMath25 + IPEDSQ1$SATMath75)/2
IPEDSQ1$SATReadAvg = (IPEDSQ1$SATRead25 + IPEDSQ1$SATRead75)/2

#Average composite scores for each test
IPEDSQ1$SATAvg = (IPEDSQ1$SATMathAvg + IPEDSQ1$SATReadAvg)/2
IPEDSQ1$ACTAvg = (IPEDSQ1$ACT25 + IPEDSQ1$ACT75)/2

#Difference from national average. Positive value means that school has high scores for that test compared to national average. 
IPEDSQ1$ACTDiff = (IPEDSQ1$ACTAvg-21)/36
IPEDSQ1$SATDiff = (IPEDSQ1$SATAvg-505)/800

#Bias towards one test or the other. High ACT bias means ACT scores are disproportionately low compared to SAT scores at that school. 
#Low ACT bias means ACT scores are disproportionately high compared to SAT scores at that school. 
IPEDSQ1$ACTBias = IPEDSQ1$SATDiff-IPEDSQ1$ACTDiff
IPEDSQ1$SATBias = IPEDSQ1$ACTDiff-IPEDSQ1$SATDiff

#Remove schools with <10 percent of students taking one test so we are only looking at schools who consider both tests. 
IPEDSQ1<-IPEDSQ1[!(IPEDSQ1$PctACT<10 | IPEDSQ1$PctSAT<10),]
order(IPEDSQ1$ACTBias)
df <-IPEDSQ1[order(IPEDSQ1$ACTBias),]
print(head(df,10))
print(head(df$ACTBias,10))
print(tail(df$ACTBias,10))
print(head(df$Name,10))
print(tail(df$Name,10))
print(mean(IPEDSQ1[["ACTBias"]]))

```
## How does the size of the institution correspond to total tuition and fees?
Important columns from the original dataset: 
  Name
  
  Applicants total
  Admissions total
  Enrolled total
  Percent admitted - total
  
  Tuition and fees, 2013-14
  
Size of institution will be represented as Enrolled total
Exclusivity will be represented as Percent admitted - total

Compare size of institution to tuition and fees
Compare exclusivity to tuition and fees
  



