---
title: "ds202_project"
author: "Rohan Mishra"
date: "4/18/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readr)
IPEDS_data
```
## creates an unscaled plot of all percentages for every zip code
```{r}
x = IPEDS_data$Name
X = IPEDS_data$`ZIP code`
y = IPEDS_data$`Percent of freshmen receiving any financial aid`
plot(X, y, main = "Zip Code To Financial Aid",
     xlab = "Zip Code", ylab = "Financial Aid (in PCT)",
     pch = 1, frame = FALSE)
```
## Creates a list of the lowest percentage students recieving financial aid
```{r}
df = data.frame(x,X,y)
newdata <- df[order(-y, x, X),]
newdata
```
## Creates a list of the highest percentage students recieving financial aid
```{r}
df = data.frame(x,X,y)
newdata <- df[order(y, x, X),]
newdata
```
## Creates a scaled plot for all percentages of students recieving financial aid per zip code
```{r}
library(ggplot2)
sp<-ggplot(IPEDS_data, aes(x, y)) + geom_point()
sp + expand_limits(x=c(0,30), y=c(0, 150))
sp
```
## Graph of students who submit SAT scores to Enrolled
```{r}
k = IPEDS_data$`Percent of freshmen submitting SAT scores`
Enrolled = IPEDS_data$`Enrolled total`
k_in_pct = k/100*n
Number_of_Students_Who_Submit_SAT = round(k_in_pct)
df2 = data.frame(Number_of_Students_Who_Submit_SAT,enrolled)
ggplot(df2, aes(x=Enrolled, y=Number_of_Students_Who_Submit_SAT, color=Enrolled)) + geom_point(size=2, shape=23) + geom_smooth(method=lm ,linetype="dashed", color="darkred", fill="blue")
```
## creates dataframe for higher SAT scores
```{r}
df3 = data.frame(x,Number_of_Students_Who_Submit_SAT,enrolled)
boop <- df3[order(x,Enrolled, -Number_of_Students_Who_Submit_SAT),]
head(boop)
```

```{r}
loop <- df3[order(Enrolled, Number_of_Students_Who_Submit_SAT,x),]
loop
```